### 2018-09-08 manuscript/manuscript.Rmd
interactions as expected

ANALYZE THE EFFECT OF RESPONSE ORDER

@@

```{r readStreakBF, echo=FALSE, message=FALSE}
 filePath<- file.path("..","E1","Results","streakBayesfactor.txt")
 con = file(filePath, "r")
 line = readLines(con, n = 1)
```

>>>>

## No effect of response order
One process that reading order can affect is memory retrieval. For readers of languages written left-to-right, readers 
When people retrieve a list of items

One way that reading order can exert its effect is by affecting the

In studies of serial-order memory, readers of European lan- guages have been shown to associate sequences of items with positions from left to right. Items presented later in a list are associated with spatial positions further to the right, even when all stimuli are presented at the same position (Rinaldi et al., 2015; van Dijck, Abrahamse, Majerus, & Fias, 2013). These studies further suggest that when people retrieve a list of items in order, they scan a mental representation from left to right, which facilitates retrieval in the correct temporal order. So far, the effect of implied reading order has not been tested in this literature, but it has been suggested that it will have an effect (Abrahamse, van Dijck, Majerus, & Fias, 2014).

In certain conditions, memory for serial order is spatialized by the human mind.

@@

```{r readStreakBF, echo=FALSE, message=FALSE}
 filePath<- file.path("..","E1","Results","streakBayesfactor.txt")
 con = file(filePath, "r")
 line = readLines(con, n = 1)
 close(con)
```
